MSF_Groupwork-NBA_shotlog

### 2016-10-10 MSFGroupwork-NBAHotHand.Rmd
1st part - Hot Hand Theory

>>>>

```
###Hot Hand Theory

```{r}
#Set the value to character
df[, "SHOT_RESULT"] <- as.character(df[, "SHOT_RESULT"])

#Define 1 for baskets made and 0 for baskets missed. We need a vector to use it to our function below.
shotresult <- c()
for(i in 1:nrow(df)) {
  if(shots[i] == 'missed') shotresult <- c(shotresult, 0)
  else if(shots[i] == 'made') shotresult <- c(shotresult, 1)
}

shotresult

#Set the value to numeric/integer
df[, "SHOT_RESULT"] <- as.numeric(df[, "SHOT_RESULT"])
df[ ,'SHOT_NUMBER'] <- as.integer(df[ , 'SHOT_NUMBER'])

#Create new column with shot results(1 for baskets made and 0 for baskets missed)
df[ ,'SHOTRESULT_0_1'] <- shotresult

#Define the length of a shooting streak to be the number of consecutive baskets made until a miss occurs
#Create a function that gives us a vector with the number of streaks
number_of_streaks <- function(x) {
  x <- c(0, x, 0)
  which_zero <- which(x == 0)
  streak <- diff(which_zero) - 1
  streak
}

number_of_streaks(shotresult)
#To be continued (probabilities- indipendence, plots, interpret results for specific players(those with higher shot_numbers))
```
